Constant Rate Computational Fuzzy Extractors

### 2014-01-07 trunk/constantRate/ConstCompFuzzExt.tex
Working on proof outline

\ifnum\shownotes=1
\newcommand{\authnote}[2]{{\textcolor{red}{\textsf{#1 notes: }\textcolor{blue}{ #2}}\marginpar{\textcolor{red}{\textbf{!!!!!}}}}}
\else
\newcommand{\authnote}[2]{}
\fi
\newcommand{\bnote}[1]{{\authnote{Ben}{#1}}}
\newcommand{\lnote}[1]{{\authnote{Leo}{#1}}}

@@

As in the information-theoretic realm~\cite[Lemma 4.1]{DBLP:journals/siamcomp/DodisORS08}, a computational fuzzy extractor can be constructed by combining a correction component and an privacy-amplication component.  As shown in Fuller, Meng, and Reyzin~\cite[Corollary 3.8 and Theorem 3.10]{fuller2013computational}, the ``right'' correction component is probably not a computational version of a secure sketch.  Instead, we will use a computational fuzzy extractor~(this is a computational analogue of the notion introduced by Kanukurthi and Reyzin~\cite{KanukurthiR09}):

\begin{definition}
Let $\mathcal{W}$ be a family of probability distributions over $\mathcal{M}$.  A pair of randomized procedures ``generate'' (\gen) and ``reproduce'' (\rep) is a $(\mathcal{M}, \mathcal{W}, \tilde{m}, t$)-computational fuzzy conductor that is $(\epsilon, s_{sec})$-hard with error $\delta$ if $\gen$ and $\rep$ satisfy the following properties:
\begin{itemize}
\item The generate procedure \gen on input $w\in \mathcal{M}$ outputs a string $Y\in\{0,1\}^\ell$ and a helper string $P\in\{0,1\}^*$.
\item The reproduction procedure \rep takes an element $w'\in\mathcal{M}$ and a bit string $P\in\{0,1\}^*$ as inputs.  The \emph{correctness} property guarantees that if $\dis(w, w')\leq t$ and $(Y, P)\leftarrow \gen(w)$, then $\Pr[\rep( w', P) = Y] \geq 1-\delta$ where the probability is over the randomness of $(\gen, \rep)$.  
If $\dis(w, w') > t$, then no guarantee is provided about the output of \rep.
\item The \emph{security} property guarantees that for any distribution $W\in \mathcal{W}$, the string $Y$ has high HILL entropy conditioned on $P$, that is $H^{\hill}_{\epsilon, s_{sec}}(Y |P)\geq \tilde{m}$.\bnote{need to define conditional HILL entropy}
\end{itemize}
\end{definition}

@@

\begin{lemma}
Let $n$ be a security parameter.  Let $W(n) = W = W_1,..., W_t$ be a distribution where each $W_i$ is independent of all $W_j$ and $\forall i, \Hoo(W_i) = \omega(\log n)$.  Let $t$ be a desired error-tolerance.  Then let $\mathcal{A}$ be an adversary making a polynomial number of oracle equality queries for blocks $i$.  %Let $C = c_1,.., c_\ell$ be as in \consref{cons:informal construction}. 
Then $\forall i, \Hav(W_i | View(A))  = \omega(\log n)$.
\end{lemma}
\begin{proof}
Consider a particular block $i$, we measure how an adversaries queries affect the entropy of this block~(we can ignore the other blocks as they are independent).  
Let $q_w$ be a query asking if the stored value is $a_w$ and its corresponding response.  
Let $Q_{w_1},A_{w_1},..., Q_{w_q}, A_{w_q}$ be the random variables representing the queries and answers for an  adversary $\mathcal{A}$ making $q$ queries.  We assume a deterministic adversary (the adversary is unbounded and thus can compute the best possible queries).  The only dependence between $W_i$ and this view of the adversary is in $A_1,..., A_q$ so we can consider these binary responses.  (There is dependency between $W_i$ and the queries but it is all contained in $A_{w_1},..., A_{w_q}$.)  Our goal is to count the total number of possible responses $A_{w_1},..., A_{w_q}$.  There are two basic cases for $A_{w_1},..., A_{w_q}$: the all zeros string and the case where some query returns $1$.  If some query $Q_{w*}$ returns $1$ then all other $Q_{w_i} = Q_{w*}$ will return $1$ but no other query returns $1$.  These responses can be removed as the response is deterministic.  Let $A'$ represent the sequence with all duplicate queries removed.  This sequence has at most a single $1$.  Thus, the total number of possible responses is $q+1$.  Thus, we have the following,
\begin{align*}
\Hav(W_i | View(A)) &= \Hav(W_i| Q_{w_1}, A_{w_1},..., Q_{w_q}, A_{w_q})\\
&=\Hav(W_i | A_{w_1},..., A_{w_q})\\
&=\Hav(W_i |A') \\
&=\Hoo(W_i) - \log |A'|\\
&= \omega(\log n) - \log |A'|\\
&= \omega(\log n) - \log (q+1) = \omega(\log n) - O(\log(n)) = \omega(\log n)
\end{align*}
Where the fourth line follows from the third by~\cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08}.
This argument holds for all $i$.  This completes the proof.
%There are two possible outcomes to an equality query $1$ in which case $\Hoo(W|Q = q_w) = 0$ and $0$ in which case $\Hoo(W| Q =q_w ) \geq -\log 2^{-\Hoo(W)}(1 - 2^{-\Hoo(W)})$~(every remaining outcome is scaled by the $w$ not being a possible outcome).  Thus,
%\begin{align*}
%\Hav(W | Q_w) &= -\log \left(\Pr[W=w]2^{-0} + \Pr[W\neq w] 2^{-\Hoo(W)}(1 - 2^{-\Hoo(W)})\right)\\
%&\geq -\log \left(2^{-k} + (1-2^{-k})2^{-k}(1-2^{-k})\right)\\
%&\geq -\log \left(2^{-(k)}(1+(1-2^{-k})^2)\right)\geq k-1
%\end{align*}
%Now consider the distribution $W' = W | W\neq w$, by the same argument asking a single query of $W'$ reduces it min-entropy by at most one bit~(we need only consider the case where previous responses were all zeros as the entropy is already $0$ if a previous response is $1$).  Thus, for some polynomial number of queries $n_q$ we have that $\Hav(W | Q_1,..., Q_{n_q}) = k - n_q$.  Thus for $k = \omega(\log n)$ and $n_q = \poly(n)$\bnote{this is too big a loss} %we have that $k-n_q = \omega(\log n)$.  This completes the proof of the lemma. 
\end{proof}
\begin{lemma}
\label{lem:super log insist by equal queries}
Let $W$ and $U$ be two distributions of super-logarithmic entropy.  Then for all adversaries $A$, $q = poly(n)$ queries, $\Delta(View(A^{\mathcal{O}_W(\cdot)}), View(A^{\mathcal{O}_U(\cdot)}))\leq \ngl(n)$.
\end{lemma}
\begin{proof}
It suffices to show that with the probability of all responses being $0$ is overwhelming.  Clearly, in the case when all responses are $0$ the views are identical, and thus the statistical distance is $0$.  \bnote{Finish this proof}
\end{proof}

@@

>>>>

\ifnum\shownotes=1
\newcommand{\authnote}[2]{{\textcolor{red}{\textsf{#1 notes: }\textcolor{blue}{ #2}}\marginpar{\textcolor{red}{\textbf{!!!!!}}}}}
\else
\newcommand{\authnote}[2]{}
\fi
\newcommand{\bnote}[1]{{\authnote{Ben}{#1}}}
\newcommand{\lnote}[1]{{\authnote{Leo}{#1}}}
\newcommand{\rnote}[1]{{\authnote{Ran}{#1}}}
\newcommand{\onote}[1]{{\authnote{Omer}{#1}}}

@@

As in the information-theoretic realm~\cite[Lemma 4.1]{DBLP:journals/siamcomp/DodisORS08}, a computational fuzzy extractor can be constructed by combining a correction component and an privacy-amplication component.  As shown in Fuller, Meng, and Reyzin~\cite[Corollary 3.8 and Theorem 3.10]{fuller2013computational}, the ``right'' correction component is probably not a computational version of a secure sketch.  Instead, we will use a computational fuzzy extractor~(this is a computational analogue of the notion introduced by Kanukurthi and Reyzin~\cite{KanukurthiR09}).  We use the common notion of HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99} extended to the conditional case~(see \defref{def:hill ent}):

\begin{definition}
Let $\mathcal{W}$ be a family of probability distributions over $\mathcal{M}$.  A pair of randomized procedures ``generate'' (\gen) and ``reproduce'' (\rep) is a $(\mathcal{M}, \mathcal{W}, \tilde{m}, t$)-computational fuzzy conductor that is $(\epsilon, s_{sec})$-hard with error $\delta$ if $\gen$ and $\rep$ satisfy the following properties:
\begin{itemize}
\item The generate procedure \gen on input $w\in \mathcal{M}$ outputs a string $Y\in\{0,1\}^\ell$ and a helper string $P\in\{0,1\}^*$.
\item The reproduction procedure \rep takes an element $w'\in\mathcal{M}$ and a bit string $P\in\{0,1\}^*$ as inputs.  The \emph{correctness} property guarantees that if $\dis(w, w')\leq t$ and $(Y, P)\leftarrow \gen(w)$, then $\Pr[\rep( w', P) = Y] \geq 1-\delta$ where the probability is over the randomness of $(\gen, \rep)$.  
If $\dis(w, w') > t$, then no guarantee is provided about the output of \rep.
\item The \emph{security} property guarantees that for any distribution $W\in \mathcal{W}$, the string $Y$ has high HILL entropy conditioned on $P$, that is $H^{\hill}_{\epsilon, s_{sec}}(Y |P)\geq \tilde{m}$.
\end{itemize}
\end{definition}

@@

\begin{lemma}
Let $n$ be a security parameter.  Let $W(n) = W = W_1,..., W_t$ be a distribution where each $W_i$ is independent of all $W_j$ and $\forall i, \Hoo(W_i) = \omega(\log n)$.  Then let $\mathcal{A}$ be an adversary making a polynomial number of oracle equality queries for blocks $i$.  %Let $C = c_1,.., c_\ell$ be as in \consref{cons:informal construction}. 
Then $\forall i, \Hav(W_i | View(A))  = \omega(\log n)$.
\end{lemma}
\begin{proof}
Consider a particular block $i$, we measure how an adversaries queries affect the entropy of this block~(we can ignore the other blocks as they are independent).  
Let $q_w$ be a query asking if the stored value is $a_w$ and its corresponding response.  
Let $Q_{w_1},A_{w_1},..., Q_{w_q}, A_{w_q}$ be the random variables representing the queries and answers for an  adversary $\mathcal{A}$ making $q$ queries.  We assume a deterministic adversary (the adversary is unbounded and thus can compute the best possible queries).  The only dependence between $W_i$ and this view of the adversary is in $A_1,..., A_q$ so we can consider these binary responses.  (There is dependency between $W_i$ and the queries but it is all contained in $A_{w_1},..., A_{w_q}$.)  Our goal is to count the total number of possible responses $A_{w_1},..., A_{w_q}$.  There are two basic cases for $A_{w_1},..., A_{w_q}$: the all zeros string and the case where some query returns $1$.  If some query $Q_{w*}$ returns $1$ then all other $Q_{w_i} = Q_{w*}$ will return $1$ but no other query returns $1$.  These responses can be removed as the response is deterministic.  Let $A'$ represent the sequence with all duplicate queries removed.  This sequence has at most a single $1$.  Thus, the total number of possible responses is $q+1$.  Thus, we have the following,
\begin{align*}
\Hav(W_i | View(A)) &= \Hav(W_i| Q_{w_1}, A_{w_1},..., Q_{w_q}, A_{w_q})\\
&=\Hav(W_i | A_{w_1},..., A_{w_q})\\
&=\Hav(W_i |A') \\
&=\Hoo(W_i) - \log |A'|\\
&= \omega(\log n) - \log |A'|\\
&= \omega(\log n) - \log (q+1) = \omega(\log n) - O(\log(n)) = \omega(\log n)
\end{align*}
Where the fourth line follows from the third by~\cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08}.
This argument holds for all $i$.  This completes the proof.
%There are two possible outcomes to an equality query $1$ in which case $\Hoo(W|Q = q_w) = 0$ and $0$ in which case $\Hoo(W| Q =q_w ) \geq -\log 2^{-\Hoo(W)}(1 - 2^{-\Hoo(W)})$~(every remaining outcome is scaled by the $w$ not being a possible outcome).  Thus,
%\begin{align*}
%\Hav(W | Q_w) &= -\log \left(\Pr[W=w]2^{-0} + \Pr[W\neq w] 2^{-\Hoo(W)}(1 - 2^{-\Hoo(W)})\right)\\
%&\geq -\log \left(2^{-k} + (1-2^{-k})2^{-k}(1-2^{-k})\right)\\
%&\geq -\log \left(2^{-(k)}(1+(1-2^{-k})^2)\right)\geq k-1
%\end{align*}
%Now consider the distribution $W' = W | W\neq w$, by the same argument asking a single query of $W'$ reduces it min-entropy by at most one bit~(we need only consider the case where previous responses were all zeros as the entropy is already $0$ if a previous response is $1$).  Thus, for some polynomial number of queries $n_q$ we have that $\Hav(W | Q_1,..., Q_{n_q}) = k - n_q$.  Thus for $k = \omega(\log n)$ and $n_q = \poly(n)$\bnote{this is too big a loss} %we have that $k-n_q = \omega(\log n)$.  This completes the proof of the lemma. 
\end{proof}
\begin{lemma}
\label{lem:super log insist by equal queries}
Let $W$ and $U$ be two distributions of super-logarithmic entropy.  Then for all adversaries $A$, $q = poly(n)$ queries, $\Delta(View(A^{\mathcal{O}_W(\cdot)}), View(A^{\mathcal{O}_U(\cdot)}))\leq \ngl(n)$.
\end{lemma}
\begin{proof}
It suffices to show that with the probability of all responses being $0$ is overwhelming.  Clearly, in the case when all responses are $0$ the views are identical, and thus the statistical distance is $0$.  \bnote{Finish this proof}
\end{proof}

@@

\appendix
\section{Computational Entropy}
HILL entropy is a commonly used computational notion of entropy \cite{DBLP:journals/siamcomp/HastadILL99}.  It was extended to the conditional case by Hsiao, Lu, Reyzin~\cite{DBLP:conf/eurocrypt/HsiaoLR07}.

\begin{definition}
\label{def:hill ent}
Let $(W, S)$ be a pair of random variables.  $W$ has 
\emph{HILL entropy} at least $k$ conditioned on $S$,
denoted $H^{\hill}_{\epsilon, s_{sec}}(W|S)\geq k$ if there exists a joint distribution $(X, S)$, such that $\Hav(X|S)\geq k$ and $\delta^{\mathcal{D}_{s_{sec}}} ((W, S),(X,S))\leq \epsilon$.
\end{definition}
